RELIKE: Reionization Effective Likelihood from Planck 2018 Data

### 2021-05-11 paper/rei.tex
finalized version for PRD submission v1

In the future, \relike\ can be extended in several ways.
Recent studies of quasars may indicate that the Universe have not been entirely ionized by $z = 6$ ($\sim$80\% ionized at $z = 6$)~\cite{Becker:2021jyx}. If this result is confirmed,
%in the future, 
the PC approach can be easily modified for a smaller $\zmin$ in a manner similar to the $\zmax$ study here.

Likewise current and future CMB experiments such as CLASS~\cite{Watts:2018etg} and LiteBIRD~\cite{Hazumi:2021yqq} may also improve on Planck and eventually provide cosmic variance limited measurements of CMB polarization on the largest scales, yielding improved reionization constraints. The same approach used here can be easily updated to capture the better constraints from these data in a joint effective likelihood. \\

>>>>

In the future, \relike\ can be extended in several ways.
Recent studies of quasars may indicate that the Universe have not been entirely ionized by $z = 6$ ($\sim$80\% ionized at $z = 6$)~\cite{Becker:2021jyx}. If this result is confirmed, the PC approach can be easily modified for a smaller $\zmin$ in a manner similar to the $\zmax$ study here.

Likewise current and future CMB experiments such as CLASS~\cite{Watts:2018etg, Watts:2019uvq} and LiteBIRD~\cite{Hazumi:2021yqq} may also improve on Planck and eventually provide cosmic variance limited measurements of CMB polarization on the largest scales, yielding improved reionization constraints. The same approach used here can be easily updated to capture the better constraints from these data in a joint effective likelihood. \\
